The \dealii{} Library, Version 9.2

### 2020-06-11 9.2/paper.tex
Deal with deprecated interfaces.
Fix the author list.

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
    Alexander V. Grayver,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Reza Rastak,
    Bruno Turcksin,
    Zhuoran Wang,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

\dealii{} can interface with many other libraries:
\todo[inline]{We picked up gingko. Anything else?}
\todo[inline]{Timo says: should we remove deprecated modules already? (nanoflann, netcdf)}
\begin{multicols}{3}
  \begin{itemize}
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item nanoflann \cite{nanoflann}
          %
          % nanoflann has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item NetCDF \cite{rew1990netcdf}
          %
          % netcdf has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use interfaces to these
libraries.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Joshua Christopher,
Ester Comellas,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Sara Tro,
Ferdinand Vanmaele,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

>>>>

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
    Marc Fehling,
    Alexander V. Grayver,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Reza Rastak,
    Ignacio Thomas,
    Bruno Turcksin,
    Zhuoran Wang,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

@@

\dealii{} can interface with many other libraries:
\begin{multicols}{3}
  \begin{itemize}
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item nanoflann \cite{nanoflann}%
          %
          % nanoflann has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item NetCDF \cite{rew1990netcdf}
          %
          % netcdf has been deprecated and will be removed for 9.3. remove
          % this line in the 9.3 release paper
          %
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries. We note that the nanoflann and NetCDF
interfaces are now deprecated and will be removed in \dealii{} version
9.3.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Joshua Christopher,
Ester Comellas,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Niklas Fehn,
Isuru Fernando,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Sara Tro,
Ferdinand Vanmaele,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.
